Journey: A Study in Unhelpful Titles (TODO: should we get a new title?)

### 2017-04-27 paper.tex
Minor edit to swapping hugepages
some changes to time section for mmap

(TODO: swapping large pages?)

@@

Figure \ref{fig:mmap_latency} shows for various microbenchmarks the time taken
per \texttt{mmap} operation as it varies with the total amount memory allocated
so far in the workload.

@@

First, when a continuous \texttt{mmap} (with the same permissions) happens the
kernel memory allocator does not need to create a new \texttt{vm\_area\_struct},
instead it modifies the adjacent \texttt{vm\_area\_struct}s to account for the
newly allocated space. This avoids the need to use the slab allocator to create
a new struct.

@@

The frag benchmark takes the most time of any benchmark. When a region of the
address space is being expanded, the kernel is forced to unmap it and map a new
area somewhere else.  This operation needs creation of a new memory area struct.
The kernel also must look through the red-black tree, though it never finds a
node which can be expanded to include the new mapping. Then, an insertion on the
tree is needed, possibly including rebalancing.

@@

Finally, rand will also search through the red-black tree first but there is a
reasonably high probability that it will find an existing mapping adjacent to
the desired mapping which can be expanded, obviating the need to create a new
struct and insert it into red-black tree.

>>>>

On systems with transparent hugepages enabled, huge pages are not swapped out in
one piece.  They are broken down to their component small pages, which are then
swapped to disk via the normal mechanisms. This is done to simplify the swapping
logic in the kernel, but results in additional overheads
\cite{corbet_transparent}.

@@

Figure \ref{fig:mmap_latency} shows for various microbenchmarks, the time taken
per \texttt{mmap} operation as it varies with the total amount memory allocated
so far by the system.

@@

First, when a continuous \texttt{mmap} (with the same permissions) happens the
kernel memory allocator does not need to create a new \texttt{vm\_area\_struct},
instead it modifies the adjacent \texttt{vm\_area\_struct}s to account for the
newly allocated space. This obviates the need to use the slab allocator to create
a new struct.

@@

The frag benchmark takes the most time of any benchmark. When a region of the
address space is being expanded, the kernel is forced to unmap it and map a new
area somewhere else.  This operation needs creation of a new memory area struct.
The kernel also must look through the red-black tree, though it never finds a
node which can be expanded to include the new mapping. Then, an insertion on the
tree is needed, possibly including rebalancing. Moreover, the exisiting texttt{
vm\_area\_struct} might need to be deleted and removed from the tree. All of these
operations ensure that frag mmap pattern takes the most amount of time.

@@

Finally, rand will also search through the red-black tree first but there is a
reasonably high probability that it will find an existing mapping adjacent to
the desired mapping which can be expanded, obviating the need to create a new
struct and insert it into red-black tree. Therefore, most of the times the time 
taken by rand benchmark is lower than strided.
